---
title: "Codebook"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Variables

The tidy data set contains 180 obs and 68 variables, its saved in text and csv file formats.  

### Variable list
* subject: ID of the subject tested (1:30)  
* activity: Activity name (WALKING, SITTING, LAYING…)  

The rest of the variables are a combination of features:  


* Domain: Time or Frequency  
* Instrument: Accelerometer or Gyroscope  
* Acceleration: Body or Gravity  
* Magnitude  
* Jerk  
* Axis: X, Y or Z direction  
* Statistical measurement: Mean or Standard Deviatio (STD)  

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(knitr)
res <- as_tibble(read.table("tidy_observations_summary.txt",header=TRUE))
kable(colnames(res), caption = "Observation variables",col.names = "Variable")

```

### Summaries calculation

Data is grouped and summarized by the average of each variable for each activity and each subject  

A 10 x 5 example is shown below  

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(knitr)
res <- as_tibble(read.table("tidy_observations_summary.txt",header=TRUE))
res[1:10,1:5]
```

